checkData

### 2023-08-23 analysis/checkData.Rmd
Update checkData.Rmd
created singlge sampleID column
and removed now obsolete 4x sample_journal_xx columns

Also changed name 'web_comments' to 'anyPPC' to more accurately reflect values and added some descriptive annotations

```{r}
d_journals <- d_journals %>%
  select(coder_id = `Coder's Initials`,
         pilot = `Are you piloting?`,
         journal = `Journal Name`,
         journal_empirical = `Does the journal publish empirical research?`,
         web_comments = `Check the article types page and check for web comments — does the journal offer any type of PPC?`,
         ppc_name_A = `A. Enter the name of the PPC type offered by the journal:`,
         ppc_name_B = `B. Enter the name of the PPC type offered by the journal:`,
         ppc_name_C = `C. Enter the name of the PPC type offered by the journal:`,
         ppc_description_A = `A. Enter the verbatim description of this type of PPC provided by the journal`,
         ppc_description_B = `B. Enter the verbatim description of this type of PPC provided by the journal`,
         ppc_description_C = `C. Enter the verbatim description of this type of PPC provided by the journal`,
         ppc_length_A = `A. Are there any length limits for this type of PPC?`,
         ppc_length_B = `B. Are there any length limits for this type of PPC?`,
         ppc_length_C = `C. Are there any length limits for this type of PPC?`,
         ppc_time_A = `A. Are there any time limits for submission of this type of PPC?`,
         ppc_time_B = `B. Are there any time limits for submission of this type of PPC?`,
         ppc_time_C = `C. Are there any time limits for submission of this type of PPC?`,
         ppc_ref_A = `A. Are there any reference limits for this type of PPC?`,
         ppc_ref_B = `B. Are there any reference limits for this type of PPC?`,
         ppc_ref_C = `C. Are there any reference limits for this type of PPC?`,
         ppc_review_A = `A. Is this type of PPC sent for independent external peer review?`,
         ppc_review_B = `B. Is this type of PPC sent for independent external peer review?`,
         ppc_review_C = `C. Is this type of PPC sent for independent external peer review?`,
         ppc_note_A = `A. Anything additional, unusual, or interesting to note?`,
         ppc_note_B = `B. Anything additional, unusual, or interesting to note?`,
         ppc_note_C = `C. Anything additional, unusual, or interesting to note?`,
         general_note = `Anything additional, unusual, or interesting to note?`,
         -starts_with("D. "), 
         -ends_with("Are there any other types of PPC in this journal? (Remember to check for web comments!)`"))

@@

```{r}
d_journals <- d_journals %>% mutate(journal = fct_recode(journal, 
                                         "MEMORY & COGNITION" = "Memory & Cognition",
                                         "JOURNAL OF COUPLE & RELATIONSHIP THERAPY-INNOVATIONS IN CLINICAL AND EDUCATIONAL INTERVENTIONS" = "Journal of Couple & Relationship Therapy"))
```

```{r}
d_journals <- d_journals %>%
  mutate(
    sample_journal_prominent = journal %in% journal_list_prominent$Journal,
    sample_journal_random = journal %in% journal_list_random$Journal,
    sample_journal_both = sample_journal_prominent & sample_journal_random,
    sample_journal_error = !sample_journal_prominent & !sample_journal_random
  )
```

```{r}
d_journals %>% 
  count(journal) %>%
  filter(n > 2)
```

>>>>

```{r}
d_journals <- d_journals %>%
  select(coder_id = `Coder's Initials`,
         pilot = `Are you piloting?`,
         journal = `Journal Name`,
         journal_empirical = `Does the journal publish empirical research?`,
         anyPPC = `Check the article types page and check for web comments — does the journal offer any type of PPC?`,
         ppc_name_A = `A. Enter the name of the PPC type offered by the journal:`,
         ppc_name_B = `B. Enter the name of the PPC type offered by the journal:`,
         ppc_name_C = `C. Enter the name of the PPC type offered by the journal:`,
         ppc_description_A = `A. Enter the verbatim description of this type of PPC provided by the journal`,
         ppc_description_B = `B. Enter the verbatim description of this type of PPC provided by the journal`,
         ppc_description_C = `C. Enter the verbatim description of this type of PPC provided by the journal`,
         ppc_length_A = `A. Are there any length limits for this type of PPC?`,
         ppc_length_B = `B. Are there any length limits for this type of PPC?`,
         ppc_length_C = `C. Are there any length limits for this type of PPC?`,
         ppc_time_A = `A. Are there any time limits for submission of this type of PPC?`,
         ppc_time_B = `B. Are there any time limits for submission of this type of PPC?`,
         ppc_time_C = `C. Are there any time limits for submission of this type of PPC?`,
         ppc_ref_A = `A. Are there any reference limits for this type of PPC?`,
         ppc_ref_B = `B. Are there any reference limits for this type of PPC?`,
         ppc_ref_C = `C. Are there any reference limits for this type of PPC?`,
         ppc_review_A = `A. Is this type of PPC sent for independent external peer review?`,
         ppc_review_B = `B. Is this type of PPC sent for independent external peer review?`,
         ppc_review_C = `C. Is this type of PPC sent for independent external peer review?`,
         ppc_note_A = `A. Anything additional, unusual, or interesting to note?`,
         ppc_note_B = `B. Anything additional, unusual, or interesting to note?`,
         ppc_note_C = `C. Anything additional, unusual, or interesting to note?`,
         general_note = `Anything additional, unusual, or interesting to note?`,
         -starts_with("D. "), 
         -ends_with("Are there any other types of PPC in this journal? (Remember to check for web comments!)`"))

@@

```{r}
d_journals <- d_journals %>% mutate(journal = fct_recode(journal, 
                                         "MEMORY & COGNITION" = "Memory & Cognition",
                                         "JOURNAL OF COUPLE & RELATIONSHIP THERAPY-INNOVATIONS IN CLINICAL AND EDUCATIONAL INTERVENTIONS" = "Journal of Couple & Relationship Therapy"))
```
Create sample ID column(s) to indicate whether in prominent, random, or both samples
```{r}
d_journals <- d_journals %>%
  mutate(
    sample_journal_prominent = journal %in% journal_list_prominent$Journal,
    sample_journal_random = journal %in% journal_list_random$Journal,
    sample_journal_both = sample_journal_prominent & sample_journal_random,
    sample_journal_error = !sample_journal_prominent & !sample_journal_random
  )

#Creates sampleID column denoting; prominent, random, or both to replace the 4 specified columns above
d_journals %>% 
  mutate(sample_journal_prominent = ifelse(sample_journal_prominent, "prominent", "random")) %>%
  mutate(sample_journal_both = ifelse(sample_journal_both, "both", "na")) %>%
  mutate(sampleID = case_when(
    sample_journal_both == "both" ~ "both",
    sample_journal_both == "na" ~ sample_journal_prominent,
    TRUE ~ sample_journal_both
  )) %>%
  select(-c(sample_journal_prominent, sample_journal_random, sample_journal_both, sample_journal_error))

Check entries to ensure secondary coding and identify anomalous entries
```{r}
d_journals %>% 
  count(journal) %>%
  filter(n > 2)
```
